Improving Outcome Predictions for Patients Receiving Mechanical Circulatory Support by Optimizing Imputation of Missing Values

### 2021-03-25 doc_ccqo/response_to_reviewers_r2.Rmd

__Response:__ In response to the reviewer's thoughtful comments, we hypothesize that different imputation strategies would lead to small or moderate improvements in downstream classification or regression models. however, the current analysis does not examine outcomes that are continuous or binary, and therefore we do not comment on those domains in the paper.

Regarding the low improvements to prognostic accuracy in Tables 4 and 5, we note that mortality and transplant events are difficult to predict using pre-implant data. We hypothesize that downstream prognostic accuracy would have increased by a larger amount if these outcomes were more correlated to the predictors that had missing values. We have added the following text on line X page Y: "Our results are limited in scope to mortality and transplant outcomes, which are difficult to predict using data collected prior to the surgery where mechanical circulatory support is applied. Future analyses should investigate whether greater improvements are obtained based on the choice of imputation strategy for outcomes with greater correlation to the predictors that are being imputed."

4. Although the authors have provided Figure 1 showing the missing patterns among three variables, the authors haven't explored the reasons why they're missing. For example, it is possible that the variables are missing from one INTERMACS center that failed to submit the data. And the variables can also be missing for a certain time period when a center hasn't fully started their data participation or the data version did not include such variables. Under this scenario, it will make sense to perform listwise deletion based on centers or time periods.

__Response__ We appreciate the reviewer's helpful suggestion. We reviewed potential mechanisms among the variables described in Figure 1. Due to the lack of indication for specific INTERMACS site in the de-identified data, we were not able to assess missingness based on center. On lines X-X of page Y, we write "Data on surgery time and CV pressure was recorded less frequently in the INTERMACS registry prior to 2014, and the  combination of missing CV pressure and surgery time is the most frequently occurring missing pattern in the current analysis (Figure 1). In addition, missing values for peripheral edema occurred more frequently in 2014-2015 due to revisions to the data collection forms. CV pressure is measured using an invasive hemodynamic procedure. Roughly 80% of the missing values for CV pressure were attributable to this procedure not being done."

<!-- table(is.na(im$pi_peripheral_edema), im$im_impl_yr) -->
<!-- table(is.na(im$im_surgery_time), im$im_impl_yr) -->

@@

5.2 Page 7 line 8: It will be good to give some examples of outcome variables Y.

__Response__: We have replaced the generic terms $Y$ and $X$ with "mortality risk" and "bilirubin"

5.3 If possible, summarize the features, pros, and cons for each strategy (e.g., aspects of imputation accuracy, scaled Brier score, c-index, calibration errors) and recommendation into one table.

__Response__: We have included a table that lists features, pros, and cons for each imputation strategy we analyzed. The table also gives a recommendation for these strategies based on data from the current analysis.

### 2021-03-25 doc_ccqo/doc_ccqo.Rmd
fake data

@@

@@

__Results__ Multiple imputation with random forests emerged as a robust strategy to impute missing values, increasing model concordance by 0.003 (25th, 75th percentile: 0.0008, 0.052) compared with imputation to the mean for mortality risk prediction using a downstream proportional hazards model. The posterior probability that single and multiple imputation using random forests would improve concordance versus mean imputation was 0.464 and >0.999, respectively.

@@

```{r inline_md_strat}

>>>>

# inline_md_strat

rspec_unscaled <- round_spec() %>% 
  round_using_decimal(digits = 4)

inline_md_strat_unscaled <- tbl_md_strat %>%
  bind_rows(.id = 'outcome') %>% 
  mutate(tbv = table_glue("{est/100} ({lwr/100}, {upr/100})", 
                          rspec = rspec_unscaled)) %>% 
  split(f = list(.$outcome,
                 .$model,
                 .$md_strat,
                 .$additional_missing_pct)) %>% 
  map(pull, tbv)

@@

# inline results for abstract

inline_auc_rf_vs_mean <- 
  inline_md_strat_unscaled$dead.auc.cph.ranger_mi.0 %>% 
  bracket_insert_left('25th, 75th percentile: ')

prob_rf_mi_gt_mean <- 
  fig_md_strat_infer$auc$probs$`Multiple imputation` %>% 
  filter(m2 == 'ranger') %>% 
  pull(prob_gt_meanmode)

prob_rf_si_gt_mean <- 
  fig_md_strat_infer$auc$probs$`Single imputation` %>% 
  filter(m2 == 'ranger') %>% 
  pull(prob_gt_meanmode)

@@

__Results__ Multiple imputation with random forests emerged as a robust strategy to impute missing values, increasing model concordance by `r inline_auc_rf_vs_mean` compared with imputation to the mean for mortality risk prediction using a downstream proportional hazards model. The posterior probability that single and multiple imputation using random forests would improve concordance versus mean imputation was `r prob_rf_si_gt_mean` and `r prob_rf_mi_gt_mean`, respectively.

@@
